Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-06-23 responses/Response2.tex
review2

\newcommand{\SG}[1]{{\color{red}SG:~#1}}
\newcommand{\SJM}[1]{{\color{orange}SM:~#1}}
\newcommand{\SW}[1]{{\color{purple}SW:~#1}}

@@

We agree with the referee that the number of $2 \cdot 10^9$ time steps may appear rather large in the first place.
However, LBM schemes can be implemented in an extremely efficient manner, especially using GPUs (note that our code, both the LBM and the finite-volume part, is entirely GPU-based).
The longest simulation presented in the manuscript which is for a fully 3D cylindrical flow took 1 day and 8 hours on a five-year old gaming GPU.

That said, the referee is right that highly viscous fluids such as, in particular, the alginate solution considered in this work, are a challenge to all LBM schemes.
We hypothesize that this is one of the reasons why such highly viscous complex fluids have been simulated with LBM before.
A possible remedy which may be considered in future work is the so-called Reynolds scaling.
Herein, the Reynolds number of the flow is artificially increased which decreases the LBM runtime without modifying the physical flow field as long as Re remains (much) smaller than 1.
We now mention this possibility above Eq. (13) in the manuscript.

@@

Aside from figures 3 and 5, which are planar geometries, all our systems are fully 3D.
This includes the cylindrical flow in figure 4. 
Even more important, it includes the RT-DC geometry shown in figure 7 and the fully three-dimensional cell in figure 8.
To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system \SG{ denote current figure as 8b, and add a standard 3D Paraview picture as 8a. }

>>>>

\newcommand{\SG}[1]{{\color{red}SG:~#1}}
\newcommand{\SJM}[1]{{\color{orange}SM:~#1}}
\newcommand{\SW}[1]{{\color{purple}SW:~#1}}
\newcommand{\RK}[1]{{\color{cyan}RK: #1}}

@@

We agree with the referee that the number of $2 \cdot 10^9$ time steps may appear rather large in the first place.
However, LBM schemes can be implemented in an extremely efficient manner, especially using GPUs (note that our code, both the LBM and the finite-volume part, is entirely GPU-based).
The longest simulation presented in the manuscript which is for a fully 3D cylindrical flow took 1 day and 8 hours on a five-year old gaming GPU.\RK{Wohlgemerkt war das der 3D Poisueille fürs Alginat (was das eigentliche Problem ist, das RT-DC mesh ist viel größer, haben wir aber mit MC gerechnet, hat 40 Minuten gedauert). Für die MC hat der 3D Poiseuille nicht ganz 5 Minuten gedauert.}

That said, the referee is right that highly viscous fluids such as, in particular, the alginate solution considered in this work, are a challenge to all LBM schemes.
We hypothesize that this is one of the reasons why such highly viscous complex fluids have been simulated with LBM before.\RK{Fehlt da ein not? Ist dann inhaltlich aber auch falsch, weil Re scaling. Es wurde nicht simuliert weil nicht stabil}
A possible remedy which may be considered in future work is the so-called Reynolds scaling.
Herein, the Reynolds number of the flow is artificially increased which decreases the LBM runtime without modifying the physical flow field as long as Re remains (much) smaller than 1.
We now mention this possibility above Eq. (13) in the manuscript.

@@

Aside from figures 3 and 5, which are planar geometries, all our systems are fully 3D.
This includes the cylindrical flow in figure 4. 
Even more important, it includes the RT-DC geometry shown in figure 7 and the fully three-dimensional cell in figure 8.
To bring out more clearly the latter aspect, we have added to figure 8 an illustration of our simulated system \SG{ denote current figure as 8b, and add a standard 3D Paraview picture as 8a. }\RK{Im Sinne von Bild von der deformierten Zelle? Oder meinst du ein anderes System wo man mehr sieht als einen unförmigen blob im nichts?}
